Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-01-03 paper/paper.tex
20200103 15:46:50

\author{\textcolor{cyan}{XXX}}
\affiliation{\textcolor{cyan}{XXX}}
\author{\textcolor{cyan}{XXX}}
\affiliation{\textcolor{cyan}{XXX}}

\author{Shun-Li Yu}
\email{slyu@nju.edu.cn}
\affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
\affiliation{Collaborative Innovation Center of Advanced Microstructures, Nanjing University, Nanjing 210093, China}
\author{Jian-Xin Li}
\email{jxli@nju.edu.cn}
\affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
\affiliation{Collaborative Innovation Center of Advanced Microstructures, Nanjing University, Nanjing 210093, China}

@@

\section{Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics. For nearest-neighbor (NN) spin-$1/2$ antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order \cite{PhysRevB.42.4800,PhysRevB.46.11137}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model. It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig. \ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=$1/2$ models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}. The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}. Extensive studies of magnetic properties using neutron scattering \cite{Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031001}, muon spin relaxation ($\mu$SR) \cite{PhysRevLett.117.097201}, electron spin resonance (ESR) \cite{PhysRevLett.115.167203} reveal a possible gapless quantum spin liquid (QSL) ground state. More recently, a class of compounds \emph{AReCh}$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}. The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.

Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ ($J-K-\Gamma$) model on the triangular lattice. The $J-K-\Gamma$ model Hamiltonian is given by
\begin{equation}
    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack
    \label{eq:Hamiltonian}
\end{equation}
where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.\ref{fig:ModelDefinition}(b), and $\alpha$, $\beta$ are the remaining directions. $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges. To the best of our knowledge, no exact solution has been reported so far for the spin-$1/2$ Kitaev and/or $\Gamma$ model on the triangular lattice. Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.

\begin{figure}
    \includegraphics[width=\columnwidth]{Fig1.pdf}
    \caption{(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation. (c) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
    \label{fig:ModelDefinition}
\end{figure}

In this manuscript, by combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the $J-K-\Gamma$ model. \textcolor{red}{$\cdots\cdots$}

The rest of the paper is organized as follows: \textcolor{red}{$\cdots\cdots$}

\section{Methods}
The full anisotropic Hamiltonian \eqref{eq:Hamiltonian} is no longer exactly solvable, even for the classical case. One, therefore, either has to rely on approximate analytical method or on numerical techniques. To determine the ground state of the Hamiltonian \eqref{eq:Hamiltonian}, we employ a combination of classical Monte Cralo simulation and ED calculation. Here, we briefly describe the methods we used. For convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchanges using angles $\alpha$ and $\beta$
\begin{equation}
    J=\sin\alpha \sin\beta, \quad K=\sin\alpha \cos\beta, \quad \Gamma=\cos\alpha
    \label{eq:Parameters}
\end{equation}
where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global phase diagram.

\subsection{Classical Monte Carlo}
\textcolor{red}{A introduction to classical Monte Carlo.  To be accomplished $\cdots \cdots$}

\subsection{Exact Diagonalization}
We perform a Lanczos ED calculation of the GS energy of the Hamiltonian \eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground-state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground-state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF)
\begin{equation}
    S(\mathbf{Q}) = \frac{1}{N} \sum_{ij}e^{i\mathbf{Q}\cdot(\mathbf{R}_i - \mathbf{R}_j)} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle
    \label{eq:StaticStructureFactor}
\end{equation}
where N is the total number of spins, $\mathbf{R}_i$ is the position of site $i$ and $\langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle$ is the average over the ground state.

To extract the moment direction of a magnetic ordered phase from a cluster ground state, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
\begin{equation}
    |\Psi\rangle = \bigotimes_{i=1}^N|\theta_i,\phi_i\rangle
    \label{eq:ClusterCoherentState}
\end{equation}
where the spin-1/2 coherent state
\begin{equation}
    |\theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) |\uparrow \rangle = e^{-i\phi S^z} e^{-i\theta S^y} |\uparrow\rangle
    \label{eq:Spin-1/2CoherentState}
\end{equation}
is fully polaried along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig. \ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z |\uparrow \rangle = \frac{1}{2}|\uparrow \rangle$. By calculating the overlap with the exact cluster GS, and maximizing the probability $P = |\langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.

\section{Classical Analysis}
To understand the effects of inculding the off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension. On our proceeding, we note that the global phase diagram has been obtained previously by using a combination of Luttinger-Tsiza (LT) and classical Monte Carlo simulations \cite{PhysRevB.92.165108}. Six different magnetic orderings: ferromagnet (FM), stripe, 120$^\circ$ N\'{e}el order, nematic, $\mathbb{Z}_2$ and dual-$\mathbb{Z}_2$ vortex crystal phases were found, see Fig. 2 in Ref \onlinecite{PhysRevB.92.165108}. Our classical Monte Carlo study give qualitatively the same phase diagram.

\subsection{Moment direction of the classcial FM order}
For the classical FM order, the energy of the $J-K-\Gamma$ model per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2\Gamma(S^xS^y + S^yS^z + S^zS^x)
    \label{eq:EcFM}
\end{equation}
where $S^x$, $S^y$, $S^z$ are the corresponding components of the classical moment vector. On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\mathbf{S}| = 1$. $f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\mathbf{S}| = 1$ are fulfilled. The condition $S^x + S^y + S^z = 0$ specify a plane that is perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig. \ref{fig:ModelDefinition}(c) this is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the moment would perpendicular to the lattice plane.

Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig. 2 in Ref \onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term. For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found. When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix A for details). Based on these observation, it is reasonable to say that the ground state of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions. For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM order as the ground state which was verified by our Monte Carlo simulation. On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS. In fact, the classical GS were found to be disordered for $0 < J \ll \Gamma$ and stripe ordered for $0 < J \ll -\Gamma$. As for the disordered phase, when quantum flucations are involved, a quantum spin liquid state may emerge.

\subsection{Moment direction of the classcial stripe order}
In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig. \ref{fig:PhaseDiagram}(b)-(d). For the spin configuration shown in Fig. \ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian \eqref{eq:Hamiltonian} is
\begin{IEEEeqnarray}{rCl}
    E_{StripeX}^{c} & = & -(J + K) + 2 K S^x S^x \nonumber \\
        && \negmedspace {} + 2 \Gamma (S^y S^z - S^z S^x - S^x S^y)
    \label{eq:EcStripeX}
\end{IEEEeqnarray}
and the energy for spin configuration in Fig. \ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$. The moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$. In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
\begin{align}
    &\mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0 \label{eq:S0} \\
    &\mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y} \label{eq:S1} \\
    &\mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y} \label{eq:S2}
\end{align}
see Appendix B for their explicit expressions.

For $\Gamma=0, K>0$, it can be clearly seen from Eq\eqref{eq:EcStripeX} that the stripe order shown in Fig. \ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction. When $\Gamma=0, K<0$, the moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{S}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.

>>>>

\author{\textcolor{cyan}{XXX}}
\affiliation{\textcolor{cyan}{XXX}}

\author{\textcolor{cyan}{XXX}}
\affiliation{\textcolor{cyan}{XXX}}

\author{Shun-Li Yu}
\email{slyu@nju.edu.cn}
\affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
\affiliation{Collaborative Innovation Center of Advanced Microstructures, Nanjing University, Nanjing 210093, China}

\author{Jian-Xin Li}
\email{jxli@nju.edu.cn}
\affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
\affiliation{Collaborative Innovation Center of Advanced Microstructures, Nanjing University, Nanjing 210093, China}

@@

\section{\label{sec:SectionI}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics. For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order \cite{PhysRevB.42.4800,PhysRevB.46.11137}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model. It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}$=1/2 moments. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}. The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}. Extensive studies of magnetic properties using neutron scattering \cite{Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031001}, muon spin relaxation ($\mu$SR) \cite{PhysRevLett.117.097201}, electron spin resonance (ESR) \cite{PhysRevLett.115.167203} reveal a possible gapless quantum spin liquid (QSL) ground state. More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}. The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.

Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ ($J-K-\Gamma$) model on the triangular lattice. The $J-K-\Gamma$ model Hamiltonian is given by
\begin{equation}
    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack \label{eq:Hamiltonian}
\end{equation}
where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(b), and $\alpha$, $\beta$ are the remaining directions. $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges. To the best of our knowledge, no exact solution has been reported so far for the spin-1/2 Kitaev and/or $\Gamma$ model on the triangular lattice. Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.

\begin{figure}
    \includegraphics[width=\columnwidth]{Fig1.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation. (c) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
\end{figure}

The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization methods are introduced in Sec.~\ref{sec:SectionII}. Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states. The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a discussion of its phases. In Sec.~\ref{sec:SectionV}, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.

\section{\label{sec:SectionII}Methods}
The full anisotropic Hamiltonian~\eqref{eq:Hamiltonian} is no longer exactly solvable, even for the classical case. One, therefore, either has to rely on approximate analytical method or on numerical techniques. To determine the ground state of the Hamiltonian~\eqref{eq:Hamiltonian}, we employ a combination of classical Monte Cralo simulation and ED calculation. Here, we briefly describe the methods we used. For convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchanges using spherical angles $\alpha$ and $\beta$
\begin{equation}
    J = \sin\alpha \sin\beta, \quad
    K = \sin\alpha \cos\beta, \quad
    \Gamma = \cos\alpha \label{eq:Parameters}
\end{equation}
where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global phase diagram.

\subsection{\label{sec:SectionIIA}Classical Monte Carlo}
\textcolor{red}{A introduction to classical Monte Carlo. To be accomplished $\cdots \cdots$}

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform a Lanczos ED calculation of the GS energy of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF)
\begin{equation}
    S(\bm{Q}) = \frac{1}{N} \sum_{ij} e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle \label{eq:SMSF}
\end{equation}
where N is the total number of spins, $\bm{R}_i$ is the position of site $i$ and $\langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle$ is the average over the ground state.

To extract the moment direction of a magnetic ordered phase from a cluster ground state, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
\begin{equation}
    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
\end{equation}
where the spin-1/2 coherent state
\begin{equation}
    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
\end{equation}
is fully polaried along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$. By calculating the overlap with the exact cluster GS, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.

\section{\label{sec:SectionIII}Classical Analysis}
To understand the effects of inculding the off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension. On our proceeding, we note that the global phase diagram has been obtained previously by using a combination of Luttinger-Tsiza (LT) and classical Monte Carlo simulations \cite{PhysRevB.92.165108}. Six different magnetic orderings: ferromagnet (FM), stripe, 120$^\circ$ N\'{e}el order, nematic, $\mathbb{Z}_2$ and dual-$\mathbb{Z}_2$ vortex crystal phases were found, see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}. Our classical Monte Carlo study give qualitatively the same phase diagram.

\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
For the classical FM order, the energy of the $J-K-\Gamma$ model per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (S^x S^y + S^y S^z + S^z S^x) \label{eq:EcFM}
\end{equation}
where $S^x$, $S^y$, $S^z$ are the corresponding components of the classical moment vector. On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\bm{S}| = 1$. $f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\bm{S}| = 1$ are fulfilled. The condition $S^x + S^y + S^z = 0$ specify a plane that is perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c) this is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the moment would perpendicular to the lattice plane.

Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term. For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found. When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix A for details). Based on these observation, it is reasonable to say that the ground state of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions. For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM order as the ground state which was verified by our Monte Carlo simulation. On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS. In fact, the classical GS were found to be disordered for $0 < J \ll \Gamma$ and stripe ordered for $0 < J \ll -\Gamma$. As for the disordered phase, when quantum flucations are involved, a quantum spin liquid state may emerge.

\subsection{\label{sec:SectionIIIB}Moment direction of the classcial stripe order}
In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.~\ref{fig:PhaseDiagram}(b)-(d). For the spin configuration shown in Fig.~\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} is
\begin{eqnarray}
    E_{StripeX}^{c} & = & -(J + K) + 2 K S^x S^x \nonumber \\
        & & +\: 2 \Gamma (S^y S^z - S^z S^x - S^x S^y) \label{eq:EcStripeX}
\end{eqnarray}
and the energy for spin configuration in Fig.~\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$. The moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$. In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
\begin{subequations}
    \label{eq:whole}
    \begin{align}
        & \mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0 \label{eq:S0} \\
        & \mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y} \label{eq:S1} \\
        & \mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y} \label{eq:S2}
    \end{align}
\end{subequations}
see Appendix B for their explicit expressions.

For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction. When $\Gamma=0, K<0$, the moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{S}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.
